\section{Introduction}

Recent advances in cloud and distributed computing enabled Big Data 
processing. Today, processing big data generally falls under the category 
of statistical inferencing, e.g., predicting congestion with traffic data 
in the road network. The bottleneck is mainly the system I/O capacity for 
reading and writing data. The computation applied to individual items is 
relatively simple compared to the amount of data to process. 

However, big data processing will ultimately require large scale 
optimizations in the future. For example, one might want to optimize the 
traffic light system of an entire city using predictions. 
Unfortunately, the traditional optimization algorithms are fundamentally hard to parallelize. These algorithms are hard to scale and cannot run on existing cloud environment. 

In recent years, several abstractions using belief propagation (BP), a popular class of distributed machine learning algorithm, to 
parallelize linear optimizations have been proposed~\cite{BPLP, BPLPmatching}. 
Several well known optimization problems - the matching problem~\cite{BPmatching} and min-cost network flow problem~\cite{BPflow} - were relaxed to a Linear Program (LP) then solved through BP in certain cases. 

The goal of this research is to develop a practical system that runs on modern cloud environments, such as Amazon EC2, for parallel, distributed optimizations on maximum weight matching (MWM) problems. 
We plan to enhance recent theoretical developments on BP for large-scale linear optimizations and and develop a cloud-based software to solve MWM problems using the power of large-scale cloud computing.
